BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2013-12-12 tex/5-evaluation.tex
Up

% setup
Experimental data was obtained by taking the arithmetic mean over 10 measurements, which we believe to be significant given that standard deviations are of the order of 2 milliseconds.

\autoref{runningtime} shows the cumulated time spent for each article extraction procedure (this excludes common tasks such as downloading pages and storing results) as a function of the number of blog posts processed. We used the Quantum Diaries \cite{quantumdiaries} blog for this experiment.

@@

Past the initial computations, the cost of processing a blog post with our approach is almost zero. This is a consequence of having a blog-aware, rule-based algorithm. As already mentioned, the central idea is to first build extraction rules using the information provided by the web feed, and then use these rules on all posts of the blog. The initial increase in the curve of our approach corresponds to the computation of the extraction rules, which consists of processing the web feed and all the blog posts it references. Subsequent computations only involve parsing blog posts and applying extraction rules, which takes about 3 milliseconds and are barely visible on the scale of \autoref{runningtime}. The other evaluated solutions do not function this way: each blog post is processed as new and independent input, leading to approximatly linear running times.

>>>>

% the graph
\autoref{runningtime} shows the cumulated time spent for each article extraction procedure (this excludes common tasks such as downloading pages and storing results) as a function of the number of blog posts processed. We used the Quantum Diaries \cite{quantumdiaries} blog for this experiment.

% standard deviations
Data presented in this graph was obtained by taking the arithmetic mean over 10 measurements. These results are believed to be significant given that standard deviations are of the order of 2 milliseconds.

@@

Past the initial computations, the cost of processing a blog post with our approach is almost zero. This is a consequence of having a blog-aware, rule-based algorithm. As already mentioned, the central idea is to first build extraction rules using the information provided by the web feed, and then use these rules on all posts of the blog. The initial increase in the curve of our approach corresponds to the computation of the extraction rules, which consists of processing the web feed and all the blog posts it references. Subsequent computations only involve parsing blog posts and applying extraction rules, which takes about 3 milliseconds and are barely visible on the scale of \autoref{runningtime}. The other evaluated solutions do not function this way: each blog post is processed as new and independent input, leading to approximately linear running times.
